\chapter*{Preface}
\setheader{Preface}

This report, along with the two scientific articles present in it, is the culmination of the work I did for my Master's thesis. First, I would like to thank my supervisor and mentor, Dr.~Hadi Jamali-Rad, for the constant guidance and support. Much of this work would not have come to fruition if not for Hadi's drive and impeccable attention to detail. Not only has Hadi taught me whatever I know about the art of research, but he also imparted valuable life lessons that will always stay with me.

I would like to express my gratitude to my parents, brother and girlfriend. Without whose support, understanding and encouragement, I would not have the privilege of being able to pursue my interests or write this report while sitting in Delft.

Finally, I would like to thank the thesis committee chair, Dr.~Jan van Gemert, for his fantastic and exciting Deep Learning and Computer Vision classes that I always looked forward to attending. I would also like to thank Dr.~Elvin Isufi for their time and interest in my work, particularly during a busy and sweltering summer.

I am glad to have met some of the brightest people I know in Delft, and some have become my close friends. I cherish all my moments with them, especially the time spent in building 28. Thank you for making this journey colourful.

Working through my thesis, I have realised that my passion for computer science and research remains stronger than ever before.

This report has been structured to first show the two scientific articles containing the motivation, explanations, methods developed, and experimental results. The chapters following the articles present the fundamental concepts that have made this work a reality. The report has been designed to be as self-contained as possible.

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Delft, August 2022
\makeatother}
\end{flushright}